Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-02 conclusions.tex
commented some text in the conclusion
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@812 ccdd05d5-56c1-461a-bf98-85f6876523b4
removed missing reference
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@839 ccdd05d5-56c1-461a-bf98-85f6876523b4

We have demonstrated a computationally feasible procedure for the rapid
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar-mass black holes.  These sources are expected to produce
prompt electromagnetic signals and may be the progenitors of some short hard
gamma-ray bursts.  Rapid alerts to the broader astronomical community may
improve the chances of detecting an electromagnetic counterpart in bands from
X-ray down to radio.  We antipate requiring no more than \numcpus\ modern
computer cores to analyze a four-detector network of gravitational-wave data
for such systems assuming spin effects can be ignored in parameterizing the
expected signals~\cite{the-papers-that-say-that-is-okay}.  This is within the
current computing capabilities of the \textsc{lsc} Data Grid~\cite{LDG}.

@@

Latency budget, including `before' and `after' quotes for:

\begin{itemize}
\item Data acquisition
\item Calibration
\item Data aggregation
\item Analysis
\item Localization
\item Alert
\item Telescope actuation
\item Total
\end{itemize}

Future work:

\begin{itemize}
\item Sub-solar mass search
\item Hierarchical detection
\end{itemize}

>>>>

We have demonstrated a computationally feasible procedure for the rapid
detection of gravitational waves emitted during the coalescence of neutron
stars and stellar-mass black holes.  These sources are expected to produce
prompt electromagnetic signals and may be the progenitors of some short hard
gamma-ray bursts.  Rapid alerts to the broader astronomical community may
improve the chances of detecting an electromagnetic counterpart in bands from
X-ray down to radio.  We antipate requiring no more than \numcpus\ modern
computer cores to analyze a four-detector network of gravitational-wave data
for binary neutron stars and stellar mass black holes.  This is within the
current computing capabilities of the \textsc{lsc} Data Grid~\cite{LDG}.

@@

%Latency budget, including `before' and `after' quotes for:

%\begin{itemize}
%\item Data acquisition
%\item Calibration
%\item Data aggregation
%\item Analysis
%\item Localization
%\item Alert
%\item Telescope actuation
%\item Total
%\end{itemize}

%Future work:

%\begin{itemize}
%\item Sub-solar mass search
%\item Hierarchical detection
%\end{itemize}
